\textbf{Proof Reconstruction in Classical Propositional Logic}

### 2017-11-16 slides/Jonathan-Proof-Reconstruction.tex
[ slides ] fixing compilation.
minor changes.
fixed slides
[ Slides ] preparing new ones.
[ slides ] lots of changes.
[ slides ] last changes.

% --------------------------------------------------------------------------
% Color definitions.
% --------------------------------------------------------------------------
\usepackage{xcolor}
\definecolor{aliceblue}{rgb}{0.94, 0.97, 1.0}
\definecolor{amber}{rgb}{1.0, 0.75, 0.0}
\definecolor{amethyst}{rgb}{0.6, 0.4, 0.8}
\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
\definecolor{ashgrey}{rgb}{0.7, 0.75, 0.71}
\definecolor{ballblue}{rgb}{0.13, 0.67, 0.8}
\definecolor{blue(munsell)}{rgb}{0.0, 0.5, 0.69}
\definecolor{blue(pigment)}{rgb}{0.2, 0.2, 0.6}
\definecolor{blu}{RGB}{1,0,102}
\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
\definecolor{brightmaroon}{rgb}{0.76, 0.13, 0.28}
\definecolor{cadet}{rgb}{0.33, 0.41, 0.47}

@@

\setbeamerfont{frametitle}{size=\small,series=\bfseries}
\setbeamercolor{frametitle}{fg=white,bg=plum}

\setbeamerfont{framesubtitle}{size=\normalfont\scriptsize}
\setbeamercolor{framesubtitle}{fg=white, bg=plum!80!black}

@@

,

@@

@@

\begin{minted}{cagda}
data Prop : Set where
  Var : Fin n → Prop
  ⊤   : Prop
  ⊥   : Prop
  _∧_ : (φ ψ : Prop) → Prop
  _∨_ : (φ ψ : Prop) → Prop
  _⇒_ : (φ ψ : Prop) → Prop
  _⇔_ : (φ ψ : Prop) → Prop
  ¬_  : (φ : Prop)   → Prop
\end{minted}
\end{itemize}
\end{frame}

>>>>

% --------------------------------------------------------------------------
% Color definitions.
% --------------------------------------------------------------------------
\usepackage{xcolor}
\definecolor{aliceblue}{rgb}{0.94, 0.97, 1.0}
\definecolor{amber}{rgb}{1.0, 0.75, 0.0}
\definecolor{amethyst}{rgb}{0.6, 0.4, 0.8}
\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
\definecolor{ashgrey}{rgb}{0.7, 0.75, 0.71}
\definecolor{background}{RGB}{1,0,102}
\definecolor{ballblue}{rgb}{0.13, 0.67, 0.8}
\definecolor{bline}{RGB}{255, 255, 255}
\definecolor{blue(munsell)}{rgb}{0.0, 0.5, 0.69}
\definecolor{blue(pigment)}{rgb}{0.2, 0.2, 0.6}
\definecolor{blu}{RGB}{1,0,102}
\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
\definecolor{brightmaroon}{rgb}{0.76, 0.13, 0.28}
\definecolor{cadet}{rgb}{0.33, 0.41, 0.47}
\definecolor{decoration}{RGB}{10,164,216}
\definecolor{fontc}{RGB}{255, 255, 255}
\definecolor{logo}{RGB}{1,0,102}

@@

\setbeamerfont{frametitle}{size=\small,series=\bfseries}
\setbeamercolor{frametitle}{fg=white,bg=blue}

\setbeamerfont{framesubtitle}{size=\normalfont\scriptsize}
\setbeamercolor{framesubtitle}{fg=white, bg=blue!80!black}

@@

% --------------------------------------------------------------------------
% Listings
% --------------------------------------------------------------------------

\usepackage{minted}
\setminted[cagda]{
  bgcolor   = aliceblue
, fontsize  = \footnotesize
, frame     = none
% , framerule = 0.4pt
% , framesep  = 0pt
, style     = cagda
}

@@

\begin{frame}

@@

\begin{minted}{cagda}
data PropFormula : Set where
  Var : Fin n → Prop
  ⊤   : Prop
  ⊥   : Prop
  _∧_ : (φ ψ : Prop) → Prop
  _∨_ : (φ ψ : Prop) → Prop
  _⇒_ : (φ ψ : Prop) → Prop
  _⇔_ : (φ ψ : Prop) → Prop
  ¬_  : (φ : Prop)   → Prop
\end{minted}
\end{itemize}
\end{frame}
